%______________________________________________________________________________________________________________________

\documentclass[margin,11pt]{resume}

%______________________________________________________________________________________________________________________
\begin{document}
%\name{\Large }
\begin{resume}
\vspace{70pt}
    %__________________________________________________________________________________________________________________
    % Scholastic Achievements
    \section{\mysidestyle Scholastic\\Achievements}
   \begin{list2}
\item \textbf{All India Rank 104} (\textsl{State Rank 2}) among 3.75 lakh participants in \textsl{National Level Science Talent Search Examination (NSTSE)} \textsl{2012} conducted by Unified Council
\item Secured \textbf{All India Rank 1} in \textsl{International Olympiad of Science (IOS)} \textsl{2009}
\item \textbf{All India Rank 53} (\textsl{State Rank 1}) in \textsl{National Science Olympiad (NSO)} \textsl{2008} conducted by Eduheal Foundation amongst nearly 4 lakh participants
\item Pursuing \textbf{Minors} at \textsl{Industrial Design Centre, IIT Bombay}
\item Amongst \textbf{top 0.005\%} in AIEEE 2012, an exam taken by over a million students
 %%%%%Awarded


 \end{list2}
 
    \section{\mysidestyle Professional \\ Experience}
\textbf{Product Development Intern} \hfill \textbf{Winter 2013}\\
\textsl{Tushky Events and Entertainment}
\begin{list2}
\item Designed and implemented a \textbf{Ranking Algorithm} for various kinds of activities
\item Developed a \textbf{Facebook Application} for events calendar.
\item Implemented a \textbf{Recommendation System} based on Apache Mahout.
\end{list2}
 
 
 
    %__________________________________________________________________________________________________________________
    % Projects Undertaken
    \section{\mysidestyle Key \\ Academic Projects}
    \textbf{Chess Titans}  \hspace{5em} \textsl{Guide: Prof. Amitabha Sanyal} \hspace{8em} \textbf{Spring 2013}
\vspace{-3.5mm}
\begin{list2}
\item One player chess game in PLT Scheme using in-built GUI Toolkit in DrRacket 
\item AI makes use of the \textbf{Minimax Algorithm} with \textbf{Alpha-Beta Pruning}
\item Heuristics to decide the best move for the computer, at any stage of the game
\end{list2}
\vspace{-2mm}
\textbf{E-Ball}  \hspace{8em} \textsl{Guide : Prof. Abhiram Ranade} \hspace{7em} \textbf{Autumn 2012}
\vspace{-3.5mm}
\begin{list2}
\item Classic brick breaker game in C++ using \textbf{Particle Physics} 
\item Randomly generating levels with varying difficulty and ball speeds 
\item \textbf{User Interface} designed using the \textbf{simplecpp} package
\end{list2}

\section{\mysidestyle Other Projects}
\textbf{Rumor Roll!} \hfill \textbf{Autumn 2013}\\
\textsl{Yahoo! HackU}
\begin{list2}
\item A website that displays links, tweets and videos related to rumors about the query
\item Made in \textbf{24 hours} using \textbf{Yahoo! Boss API, Twitter API v2.0 and YouTube API}
\end{list2}
\vspace{-2.5mm}
\textbf{Android Desktop Controller} \hfill \textbf{Summer 2013}\\
\textsl{Institute Technical Summer Project (ITSP)}
\begin{list2}
\item An Android application that uses Bluetooth to control PC through an Android mobile 
\item Used Java's \textbf{Robot} class to assign PC's features to commands passed by device as strings
\end{list2}
\vspace{-2.5mm}
\textbf{Hostel Website} \hfill \textbf{Autumn 2013}\\
Developed the website for Hostel-3 (Currently Live) using \textbf{Twitter Bootstrap v2.3.2}.

\section{\mysidestyle Robotics}
\textbf{XLR8 2.0} \hfill \textbf{Spring 2013}\\
Designed our own \textbf{Football playing RC bot} from scratch and secured the \textbf{2$^{\textbf{nd}}$ position}.\\
\vspace{-2mm} \\
\textbf{Line Follower Competition} \hfill \textbf{Autumn 2012}\\
Designed and programmed an \textbf{autonomous line-following bot} by coding \textbf{Arduino} \\ microcontroller board and secured the \textbf{1$^{\textbf{st}}$ position} among a hundred participating teams.\\
\vspace{-2mm} \\
\textbf{XLR8}  \hfill \textbf{Autumn 2012}\\
Designed our own \textbf{RC bot} from scratch on the principle of motor driver circuit and awarded the \textbf{best hostel team} among nearly 200 teams. 

\pagebreak

\vspace{-150em}

\section{\mysidestyle Programming Skills}
\begin{list2}
\item \textbf{Programming Languages:} \textbf{C++, Java}, MIT-Scheme, \textbf{Python}, Prolog, \LaTeXe{}
\item \textbf{Web Development:} HTML5, CSS3, PHP, JavaScript
\item \textbf{Engineering Softwares:} MATLAB, SCILAB, LabView
\item \textbf{Environments:} Windows, Linux
\end{list2}

\section{\mysidestyle Fields of Interest}
\begin{list2}
\item Machine Learning
\item Algorithm Design and Analysis
\item Cryptography
\item Artificial Intelligence
\end{list2}
    %

\section{\mysidestyle Positions of responsibility}
\textbf{Convener}, \textsl{Web and Coding Club}, IIT Bombay \hfill \textbf{April 2013 -- Present}\\
Convener of one of the biggest clubs of IIT Bombay which supports coding and related activities in the institute, promoting coding culture across students of all departments. \\ Responsible for organising Hackathons, talks and many other coding related events
\vspace{2mm}\\
\textbf{Web Secretary}, \textsl{Hostel 3}, IIT Bombay \hfill \textbf{April 2013 -- Present}\\
Elected as Hostel Web Secretary for Hostel 3. Responsibilities include:
\begin{list2}
\item Conducting intra-hostel web development workshops and competitions.
\item Design and maintenance of the hostel website and ensuring that everything done by the hostel council is transparent and publicised through a common web portal
\end{list2}
\vspace{-3mm}
\textbf{Coordinator}, \textsl{TechFest 2014} \hfill \textbf{May 2013 -- January 2014}\\
Installed jQuery plugins on the website for TechFest 2014 and coordinated a workshop on Swarm Robotics.
%__________________________________________________________________________________________________________________

\section{\mysidestyle Extra Co-Curricular Activities}
\begin{list2}
\item Worked as a business developer for \textbf{crowdfunding} module in \textsl{StartupToday}
\item Participated in two \textbf{Model United Nations (MUN)} conferences -- \textbf{TCETMUN} 2012 by \textsl{Thakur College of Engineering} and \textbf{TIMUN 2013} by \textsl{TechFest, IIT Bombay}
\item Enthusiastic in literature, creative writing and philosophy
\item Written many blogs, including \textbf{Web Development} blogs for \textsl{Web and Coding Club}
\item Active user on \textbf{Sphere Online Judge (SPOJ)} and \textbf{HackerRank}
\item Completed the year-long course by \textbf{National Sports Organization (NSO)} in \textbf{Squash}
\item Enthusiastic in swimming and water adventure sports like Scuba
\item Worked as an organiser in Mood Indigo 2012, TechFest 2013 and E-Summit 2013
\end{list2}



    \section{\mysidestyle Key Courses Undertaken} 

	\textbf{Core:} \\ Data Structures, Abstractions and Paradigms in Programming, Software Systems*, \\ Design and Analysis of Algorithms*, Logic Design*, Computer Programming and Utilization, Discrete Mathematics, Introduction to Machone Learning \\
	\textbf{Other:} \\ Calculus, Linear Algebra, Differential Equations, Numerical Analysis*, Modern Physics, \\ Environmental Studies, Economics, Basics of Electronics and Electrical Engineering, \\ Chemistry, Basics of Visual Communications, Data Analysis and Interpretation,\\ Sound and Music Design\\
	\textbf{Online Courses:} \\ Algorithms: Part I and Part II (Prof. Robert Sedgewick and Prof. Kevin Wayne), \\ Learn to Program: The Fundamentals (Prof. Jennifer Campbell and Prof. Paul Gries), \\ Machine Learning (Prof. Andrew Ng)
\vspace{1mm}\\%
	Note: The * marked courses will be completed by April 2014.


\end{resume}
\end{document}




